---
title: "Basic usage of our standardized colours"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LLMPP.viz)
library(dplyr)
library(kableExtra)
library(ggplot2)
```

# Peek at what's available

```{r}
summarise_colours()
```

# Narrow the options down

```{r}

summarise_colours(col_category = "subgroup")

```

# Preview them

```{r}

show_colours(col_category = "subgroup")

```


# Preview just one group

```{r}

show_colours(col_group = "LymphGen")

```

# Retrieve and put them to use

In our experience, the most common use case for named colours is using ggplot2 with manual scales. This requires a named vector with names that map to each of the groups you will be setting in your aesthetic. Here's a basic example:

```{r}

lymphgen_vec = get_colours(col_group = "LymphGen")
ggplot(data.frame(x=names(lymphgen_vec)),aes(x=sample(100,length(lymphgen_vec)),
                                             y=sample(100,length(lymphgen_vec)),
                                             colour=x)) + 
  geom_point(size=3) + 
  scale_color_manual(values=lymphgen_vec) + 
  theme_minimal()

```

# Skipping the extra steps

If you are certain your data already maps to colours in the full set, there is no need to subset. You can simply provide the unfiltered output of `get_colours` to ggplot2:

```{r}
every_colour = get_colours()
length(every_colour)

ggplot(data.frame(x=names(lymphgen_vec)),
       aes(x=sample(100,length(lymphgen_vec)),
                                             y=sample(100,length(lymphgen_vec)),
                                             colour=x)) + 
  geom_point(size=3) + 
  scale_color_manual(values=every_colour) + 
  theme_minimal()

```


# See all the colours available

It may be easier for you to decide what filters to apply if you view the entire set of colours together. There are currently `r get_colours() %>% length()` distinct colours, some with multiple aliases. They can all be visualized together by running `show_colours` without any parameters.

```{r}

show_colours()

```
